---
title: "simpleRegress"
author: "Marcia Alarcon"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## INTRODUCTION

Here we are trying to find the way to predict the length of a bear.


## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

This scatterplot shows that as Neck size goes up, length does as well making the Neck size a good predictor to determine length.

Neck as variable for determining a bears lrnth had adjusted R square score of 0.7476.

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```

## NUMERICAL SUMMARY

```{r}
cor(bears$LENGTH,bears$CHEST)
```

Correlation is a relationship

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

This scatterplot shows that as CHEST size goes up, length does as well making the CHEST size a better predictor to determine length.

CHEST as a variable determining a bears l;ength had adjusted R squared score of 0.7869

## CONCLUSION

Chest is a better predictor of length than neck is because the adjusted R squared of the fit for CHEST was larger than the adjust R squared of the fit for neck

